---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(tidyverse)
library(cancensus)
library(sf)
library(geojsonsf)
library(haven)

```

# Loading client data

```{r}

# Postal code data

# Note that using the original dataset crashes on JupyterHub so we will be using break_glass_in_case_of_emergency instead. C

# Code for had we used the original dataset:
# dataset = read_sav("data-raw/pccfNat_fccpNat_082021sav.sav")
# postcode <- dataset %>% 
#   select(PC, CSDuid)

# Using break_glass_in_case_of_emergency instead
postal_code <- read_rds("data-raw/break_glass_in_case_of_emergency.Rds")

# Customer to device data
cust_dev <- read_rds("data-raw/cust_dev.Rds")

# Device data
device <- read_rds("data-raw/device.Rds")

# Customer data
customer <- read_rds("data-raw/customer.Rds")




```

# Getting external data

## Web scraping industry data

```{r}

```

# Census API

```{r}

# Retrieving income data from the 2016 Canada census

options(cancensus.api_key = "CensusMapper_f6c277b158875b85a8d9423115396b89",
        cancensus.cache_path = "cache") # this sets a folder for your cache


# get all regions as at the 2016 Census (2020 not up yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # Figure out what CSD means in Census data
  as_census_region_list()

# This can take a while
# We want to get household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD', geo_format = "sf")

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)


```


## Data Wrangling
```{r}

#Create new customer age variable
customer <- customer %>%
  mutate(dob = as.Date(dob,'%Y-%m-%d')) %>%
  mutate(age = as.numeric(difftime(Sys.Date(),dob, units = "weeks"))/52.25)



# Make sure we only have 1 row per each CSDuid-postal code pair
postal_code <- postal_code %>%
  distinct(CSDuid, PC)

# Make sure we only have 1 row per each CSDuid-median income pair
median_income <- median_income %>%
  distinct(CSDuid, hhld_median_inc)

# Incomes with postal codes
income_postal <- inner_join(x= median_income, y=postal_code, by="CSDuid")

# Customer and incomes (using postal codes)
customer_incomes <- left_join(x= customer, y= income_postal, by = c("postcode" = "PC"))

# Customers with more than 1 postcode (and hence, more than 1 income) will now be assigned the mean of those incomes
customer_incomes <- customer_incomes %>%
  group_by(cust_id) %>%
  summarise(income = mean(hhld_median_inc)) %>%
  ungroup() 
customer_incomes <- inner_join(x= customer, y=customer_incomes, by="cust_id") 

# Customer to devices with customer information
cust_dev_info <- inner_join(x= cust_dev, y=customer_incomes, by="cust_id")

# Customer to devices with customer and devices information
cust_dev_info <- inner_join(x= cust_dev_info, y=device, by="dev_id")


# Select relevant columns
cust_dev_info <- cust_dev_info %>%
  select(sex, pronouns, emoji_modifier, age, income, device_name, line, released) %>%
  subset(select=-c(cust_id))



```

## Write to Rds

```{r}

# Write to rds
write_rds(x=cust_dev_info, file="data/cust_dev_info.Rds")

```


